\subsection{Stakeholders}
As any other project, there are different type of people that have or will have a relation with this software. We will classify the by the actors, who will participate in the development part of this project, final users, who will use the resultant software in order to obtain data, and finally the beneficiaries, who will obtain benefits from all data gathered.

\subsubsection{Actors}
In order to build this project, we will need a developer who will do all different roles this project needs. This developer will be the most active person in the project as will be the responsible for deployment all project different parts.

The roles the developer will take are the project manager (scheduling and documentation), the software designer (design of the user interface), the software developer (coding part) and the software tester (testing of prototypes in order to solve bugs and improve the usability). More information about roles and their specific tasks can be seen in section \textit{\ref{sssec:humanResources} Human resources}.

Additionally this project will be directed and coordinated by Jordi Delgado from UPC, who will help to guide the developer on each phase of the project.

We will also receive help from Philipp Winter, the author of the \textit{"Censorship on Tor paper"}, and from the Tor community as this project was on their Volunteer's projects list.

\subsubsection{Users}
The software we will obtain at the end of this project is meant to be used by volunteers inside censored countries to get data of how their censors are blocking them the access to Tor or if they are using advanced techniques to read their network packets.

Also it will be used by the Tor community because this software will send them reports about all data gathered so they can develop a solution to the censorship on these countries.

\subsubsection{Beneficiaries}
Finally, the ultimate people who will benefit with this software will be the ones from censored countries as they will be allowed to use Tor to obtain privacy and be anonymous on Internet, what will give them freedom in this big network.
